Table on stock change factors per clinate zone

### 2020-12-13 ResultNotebooks/results_SOCcompare.Rmd
update results

```{r load}
library(mrcommons)
library(mrsoil)
library(magpiesets)

rev       <- "rev0.11"
outputdir <- "Output/"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev,"histManagement_h12_carbonbudget.tgz"), exdir="Data/histManagement", extras="--keep-newer-files ")

@@

SOCStock     <- dimSums(dimSums(SoilCarbon[,,"actualstate"], dim=3.3)* Landuse, dim=3)
glo_SOCStock <- dimSums(SOCStock, dim=1) 
cell2iso     <- toolGetMapping("CountryToCellMapping.csv", type = "cell")
iso_SOCStock <- toolCountryFill(toolAggregate(SOCStock, rel=cell2iso, from="celliso", to="iso", dim=1), fill=0)
iso2reg      <- read.csv2("Data/histManagement/regionmappingH12.csv")
reg_SOCStock <- toolAggregate(iso_SOCStock, rel=iso2reg, from="CountryCode", to="RegionCode")
```

Load validation data:

```{r Validation Stocks}

library(mrvalidation)

  LPJ_IPCC   <- calcOutput("ValidCarbonStocks", datasource = "LPJ_IPCC2006", aggregate="REG+GLO", try=TRUE)
  WISE       <- calcOutput("ValidCarbonStocks", datasource = "WISE", aggregate="REG+GLO", try=TRUE)
  GSOC       <- calcOutput("ValidCarbonStocks", datasource = "GSOC", aggregate="REG+GLO", try=TRUE)
  SoilGrids  <- calcOutput("ValidCarbonStocks", datasource = "SoilGrids", aggregate="REG+GLO", try=TRUE)
  LPJmL4     <- calcOutput("ValidCarbonStocks", datasource = "LPJmL4Paper", aggregate="REG+GLO", try=TRUE)

@@

library(knitr)
library(stats)
library(luplot)
library(reshape2)

SOCStock <- mbind(glo_SOCStock, reg_SOCStock)
glo_SOC  <- mbind(setNames(SOCStock[,"y2010",],"SOC Budget"), 
                  setNames(LPJmL4[,"y2010",], "LPJmL4Paper"),
                  setYears(setNames(WISE[,1,],"WISE"), "y2010"),
                  setYears(setNames(SoilGrids[,1,],"SoilGrids"),"y2010"),
                  setYears(setNames(GSOC[,1,],"GSOC"),"y2010"))

@@

saveRDS(list(comparison_table = comparison_table), paste0(outputdir,"gloSOC_comparison.rds"))

@@

```{r kable2image}
library(kableExtra)

table <- readRDS("Output/gloSOC_comparison.rds")
colnames(table[[1]])[1] <- "Model/Database"
colnames(table[[1]])[5] <- "Global SOC in GtC"
save_kable(kable_styling(kable(table$comparison_table[c(1,5)], "latex", digit=2), latex_options = c("striped", "scale_down")), 
         file="Output/Images/TableSOC_comparison.png")

save_kable(kable_styling(kable(table$comparison_table[setdiff(1:13,5)], "latex", digit=2), latex_options = c("striped", "scale_down")), 
         file="Output/Images/TableRegSOC_comparison.png")

@@

supp.labs <- getNames(glo_SOC["GLO",,invert=TRUE])
names(supp.labs) <- c("OJ", "VC")

leg_name <- "Data Source"

glob <- ggplot(data = as.data.frame(glo_SOC["GLO",,][,"y2010",]/1000), aes(Year,Value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  scale_size_manual(values=c(4,2,2,2,2)) + 
  scale_shape_manual(values=c(19,6,2,5,0)) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  xlab("") + ylab("SOC (0-30cm) in GtC")

comp <- ggplot(data = as.data.frame(glo_SOC["GLO",,invert=TRUE][,"y2010",]/1000), aes(Year,Value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  facet_wrap(~ Region, scales="free", drop=TRUE) + 
  scale_size_manual(values=c(4,2,2,2,2)) + 
  scale_shape_manual(values=c(19,6,2,5,0)) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  xlab("") + ylab("SOC (0-30cm) in GtC")

@@

ggsave(paste0(outputdir,"/glo_comparisonfigure.png"), plot=glob, height=6, width=3, units="cm")
ggsave(paste0(outputdir,"/reg_comparisonfigure.png"), plot=comp)

>>>>

```{r load}
library(magclass)
library(madrat)

outputdir <- "Output/"

@@

SoilCarbon[,,c("naturalstate.crop")] <- SoilCarbon[,,c("naturalstate.natveg")]
SOCStock     <- dimSums(dimSums(SoilCarbon[,,c("naturalstate","actualstate")], dim=3.3)* Landuse, dim=3.2)
cell2reg     <- read.csv("Data/histManagement/ClimateZoneMapping.csv")
reg_SOCStock <- toolAggregate(SOCStock, rel=cell2reg, from="cell", to="IPCC")
```

@@

  WISE       <- readRDS("Data/histManagement/WISE.rds")
  GSOC       <- readRDS("Data/histManagement/GSOC.rds")
  SoilGrids  <- readRDS("Data/histManagement/SoilGrids.rds")
  LPJmL4     <- readRDS("Data/histManagement/LPJmL4.rds")

library(knitr)
library(stats)
library(reshape2)

SOCStock <- reg_SOCStock
reg_SOC  <- mbind(setNames(SOCStock[,"y2010","actualstate"],"This Study"),
                  setNames(SOCStock[,"y2010","naturalstate"],"This Study (PNV)"),
                  setNames(LPJmL4[,"y2010",], "LPJmL4Paper"),
                  setYears(setNames(WISE[,1,],"WISE"), "y2010"),
                  setYears(setNames(SoilGrids[,1,],"SoilGrids"),"y2010"),
                  setYears(setNames(GSOC[,1,],"GSOC"),"y2010"))
glo_SOC <- mbind(setCells(dimSums(reg_SOC, dim=1),"GLO"), reg_SOC)

@@

comparison_table$Year <- "2010"

saveRDS(object = comparison_table, paste0(outputdir,"gloSOC_comparison.rds"))

@@

```{r kable2image}
# library(kableExtra)
# 
# table <- readRDS("Output/gloSOC_comparison.rds")
# colnames(table)[1] <- "Model/Database"
# colnames(table)[6] <- "Global SOC in GtC"
# save_kable(kable_styling(kable(table$comparison_table[c(1,5)], "latex", digit=2), latex_options = c("striped", "scale_down")), 
#          file="Output/Images/TableSOC_comparison.png")
# 
# save_kable(kable_styling(kable(table$comparison_table[setdiff(1:13,5)], "latex", digit=2), latex_options = c("striped", "scale_down")), 
#          file="Output/Images/TableRegSOC_comparison.png")

@@

table    <- readRDS("Output/gloSOC_comparison.rds")
leg_name <- ""

names(table) <- c("Data1","Boreal Dry", "Boreal Moist", "C-Temp Dry", "C-Temp Moist","GLO","Polar Dry", "Polar Moist",
                  "Tropical Dry", "Tropical Moist", "Tropical Montane", "Tropical Wet", "W-Temp Dry", "W-Temp Moist", "Year")
table        <- table[,c(1,15,6,7,8,2,3,4,5,13,14,9,10,11,12)]

cols   <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7")[c(7,3,1,4,6,8)]

glob <- ggplot(data = melt(subset(table, select =c(Data1, GLO, Year))), aes(x=Year,y=value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  scale_size_manual(values=c(4,2,2,2,2,2)) + 
  scale_shape_manual(values=c(19,16,6,2,5,0)) +
  scale_color_manual(values = cols) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  xlab("") + ylab("SOC (0-30cm) in GtC") +
  theme(axis.ticks.x=element_blank(),
        axis.text.x=element_blank(), 
        legend.position="right") + guides(fill=guide_legend(ncol=1,byrow=TRUE))
        #legend.position="bottom") + guides(fill=guide_legend(nrow=2,byrow=TRUE))

comp <- ggplot(data = melt(subset(table, select=-GLO)), aes(x=Year,y=value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  facet_wrap(~ variable, scales="free", drop=TRUE, labeller = label_wrap_gen(width=8)) + 
  scale_size_manual(values=c(4,2,2,2,2,2)) + 
  scale_shape_manual(values=c(19,16,6,2,5,0)) +
  scale_color_manual(values = cols) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  xlab("") + ylab("SOC (0-30cm) in GtC") +
  theme(axis.ticks.x=element_blank(),
        axis.text.x=element_blank())

@@

ggsave(paste0(outputdir,"/Images/glo_comparisonfigure.png"), plot=glob, height=8, width=8, units="cm", dpi = 300)
ggsave(paste0(outputdir,"/Images/reg_comparisonfigure.png"), plot=comp, height=10, width=14, units="cm", dpi = 300)

### 2020-12-13 ResultNotebooks/results_SOCscenario.Rmd
update results

rev <- "rev0.11"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")

filesNeeded <- c("SoilCarbon.rds","Landuse.rds")

scenarios    <- c("histManagement","constManagement-1975", "constTillage-mixedtill", "constResidues-1975", "constManure-1975",
                  "constManagement2-1975", "constResrate-1975", "constYield-1975",
                 "Initial-natveg", "Initial-natveg_constManagement-1975", "Initial-natveg_constManagement2-1975", 
                 "LitterPNV-PerennialGrasses", "LitterPNV-AASS", "LitterPNV-BRCF", 
                 "LitterPNV-MTCF", "LitterPNV-BLEAF",  "LitterPNV-TREF")

# untar(paste0(getConfig("outputfolder"),"/", rev, "histManagement_h12_carbonbudget.tgz"), 
#       exdir="Data/histManagement", extras="--keep-newer-files ")
# 
# for(item in scenarios){
#    untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    files=filesNeeded, exdir=paste0("Data/", item), extras="--keep-newer-files ")
# }

@@

Calc global numbers

>>>>

rev         <- "rev16"
scenarios   <- c("histManagement","constManagement-1975", "constTillage-mixedtill", "constResidues-1975", "constManure-1975",
                  "constManagement2-1975", "constResrate-1975", "constYield-1975",
                 "Initial-natveg", "Initial-natveg_constManagement-1975", "Initial-natveg_constManagement2-1975", 
                 "LitterPNV-PerennialGrasses", "LitterPNV-AASS", "LitterPNV-BRCF", 
                 "LitterPNV-MTCF", "LitterPNV-BLEAF",  "LitterPNV-TREF")

# filesNeeded  <- c("SoilCarbon.rds","Landuse.rds")
# setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
# 
# untar(paste0(getConfig("outputfolder"),"/", rev, "histManagement_h12_carbonbudget.tgz"),
#       exdir="Data/histManagement", extras="--keep-newer-files ")
# 
# for(item in scenarios){
#    untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    files=filesNeeded, exdir=paste0("Data/", item), extras="--keep-newer-files ")
# }

@@

### 2020-12-13 ResultNotebooks/results_SOCtable.Rmd
update results

rev       <- "rev0.11"
outputdir <- "Output/"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data/histManagement", extras="--keep-newer-files ")

SoilCarbon <- read.magpie(paste0("Data/histManagement/SoilCarbon.rds"))[,1975:2010,]
Landuse    <- read.magpie(paste0("Data/histManagement/Landuse.rds"))[,1975:2010,]

@@

years             <- intersect(findset("past"), getYears(SoilCarbon))

### calculating climate mask
koeppen           <- readSource("Koeppen", subtype="cellular", convert="onlycorrect" )[,years,]
koepp2IPCC        <- toolGetMapping("mapping_koeppen_ipcc.csv", type = "sectoral")
getNames(koeppen)         <- tolower(getNames(koeppen))
koepp2IPCC$koeppen_geiger <- tolower(koepp2IPCC$koeppen_geiger)
climateIPCC       <- toolAggregate(koeppen, rel=koepp2IPCC, from="koeppen_geiger", to="ipcc_reduced", dim=3)
rm(koeppen)

@@

knitr::kable(SCF_table, "latex",digits=2, label="naturalstate_table")

@@

magpie_coord  <- toolGetMapping("magpie_coord.rda", type="cell")
climate2plot <- dimSums(climateIPCC*new.magpie("GLO",NULL,getNames(climateIPCC),c(1:4)), dim=3)
climate2plot <- merge(as.data.frame(climate2plot), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")

@@

cols          <- colorRampPalette(brewer.pal(4, "RdYlBu"))(4)

ClimateZones <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(climate2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = factor(Value))) +
    scale_fill_manual(name = expression("climate zones"), 
                      values = cols, na.value = "white",
                      breaks= c(1,2,3,4),
                      labels = gsub("_", " ", getNames(climateIPCC)),
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )
ClimateZones 
ggsave(paste0(outputdir,"/climatezones.png"), plot=ClimateZones , width = 10, height = 7, dpi = 300, units = "cm")
```

@@

MShare_ipcc <- LShare_ipcc <-  HShare_ipcc <- new.magpie("GLO",NULL,outer(c("IPCC2006","IPCC2019"),
                                                                          unique(koepp2IPCC$ipcc_reduced), paste, sep="."))

>>>>

rev       <- "rev16"
outputdir <- "Output/"

#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data/histManagement", extras="--keep-newer-files ")

SoilCarbon <- read.magpie(paste0("Data/histManagement/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/histManagement/Landuse.rds"))

@@

years             <- findset("past")
climateIPCC       <- readRDS("Data/histManagement/IPCC_reduced.rds")

@@

@@

climateIPCCr       <- readRDS("Data/histManagement/IPCC_reduced.rds")
climateIPCC        <- readRDS("Data/histManagement/IPCC.rds")

getNames(climateIPCC) <- c( "W-Temp Moist","W-Temp Dry","C-Temp Moist","C-Temp Dry","Polar Moist","Polar Dry","Boreal Moist",
                            "Boreal Dry","Tropical Montane","Tropical Wet","Tropical Moist", "Tropical Dry")

climateIPCC <- climateIPCC[,,c(5,7,3,1,6,8,4,2,9,11,10,12)]

magpie_coord <- toolGetMapping("magpie_coord.rda", type="cell")
climate2plot <- dimSums(climateIPCC*new.magpie("GLO",NULL,getNames(climateIPCC),c(1:12)), dim=3)
climate2plot <- merge(as.data.frame(climate2plot), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")

@@

blucols          <- brewer.pal(9, "Blues")[2:5]
viocols          <- brewer.pal(9, "Purples")[6:9]
redcols          <- brewer.pal(9, "Reds")[6:8]
orgcols          <- brewer.pal(9, "Oranges")[3]
cols <- c(blucols,viocols,redcols,orgcols)

ClimateZones <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(climate2plot, select=c("lon","lat","Value")), aes(x = lon, y = lat, fill = factor(Value))) +
    scale_fill_manual(name = "", 
                      values = cols, na.value = "white",
                      breaks= c(1,2,3,4,5,6,7,8,9,10,11,12),
                      labels = getNames(climateIPCC),
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
   scale_color_manual(values=cols) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          ) + guides(fill=guide_legend(nrow=2,byrow=FALSE))
ClimateZones 
ggsave(paste0(outputdir,"/Images/climatezones.png"), plot=ClimateZones , width = 20, height = 14, dpi = 300, units = "cm")
```

@@

MShare_ipcc <- LShare_ipcc <-  HShare_ipcc <- new.magpie("GLO",NULL,outer(c("IPCC2006","IPCC2019"),
                                                                          getNames(climateIPCC), paste, sep="."))
